\documentclass{article}
\usepackage{geometry}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\graphicspath{ {images/} }
\geometry{a4paper, left=20mm, right=20mm, top=25mm, bottom=25mm}

\title{Version-Control-Supervisor-Feedback-PoC}
\author{Jeremy Amin}
\date{November 2019}

%\pagestyle{plain}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{J. Amin - 42107881}
\lhead{FOAR705 - Supervisor Feedback PoC}
\lfoot{Session 2, 2019 - Macquarie University}
\rfoot{\thepage}

\usepackage[colorlinks=true,linkcolor=blue]{hyperref}
\usepackage{hyperref}

\begin{document}

\maketitle
\tableofcontents

\pagebreak

\section{1}

Consider a situation where Mary is hungry. In this situation, it is good for Mary to eat an apple and Mary has a right to acquire an apple to eat. It is considered bad for Mary to eat and swallow shards of glass in this scenario and it would be a duty other people have to not feed her shards of glass, and Mary would have some kind of authority to impose onto others her right to not be coerced into being force fed glass. In this scenario, the apple is valuable to Mary and the glass is not valuable. We would say that the value of the apple or the glass is relative to some feature of the scenario which is more fundamental, in this case the life and health of Mary herself. Mary is more valuable than the food which she consumes, and this is because Mary as the being who is doing the eating is that which we make the judgement of better and worse, and good and bad, about. The food is good for Mary, the apple is valuable for Mary’s health and wellbeing, and so on. From this analysis, the health and existence of Mary are more valuable than the food which she eats. The food is merely an instrumental good consumed for the sake of something more valuable than the food itself, namely Mary herself. Mary on this analysis is the entity which has intrinsic value, her life an intrinsic good.

\end{document}
